### 2022-03-13 sections/systematic_uncertainties.tex

The hdamp parameter (which controls the amount of radiation produced by the parton shower in
POWHEG-BOX v2) is set to 1.5$m_t$ in the nominal case. Alternative samples are generated with hdamp=3$m_t$. The
difference between two samples is treated as one of the systematics as ``$t\bar{t}$ hdamp''. 
%The uncertainty associated with the choice of NLO generator is derived by comparing the nominal prediction from
%{\powheg}+{\pythiaeight} with a prediction from \textsc{Sherpa}~2.2.1. For the latter, the matrix-element calculation is performed 
%for up to two partons at NLO and up to four partons at LO using \textsc{Comix} and \textsc{OpenLoops}, and
%merged with the {\sherpa} parton shower using the ME+PS@NLO prescription.

>>>>

The $h_{\mathrm{damp}}$ parameter (which controls the amount of radiation produced by the parton shower in
POWHEG-BOX v2) is set to 1.5$m_t$ in the nominal case. Alternative samples are generated with $h_{\mathrm{damp}}$=3$m_t$. The
difference between two samples is treated as one of the systematics as ``$t\bar{t}$ $h_{\mathrm{damp}}$''. 
%The uncertainty associated with the choice of NLO generator is derived by comparing the nominal prediction from
%{\powheg}+{\pythiaeight} with a prediction from \textsc{Sherpa}~2.2.1. For the latter, the matrix-element calculation is performed 
%for up to two partons at NLO and up to four partons at LO using \textsc{Comix} and \textsc{OpenLoops}, and
%merged with the {\sherpa} parton shower using the ME+PS@NLO prescription.
